Assessing United States county-level exposure for research on tropical cyclones and human health

### 2019-01-27 writing/ehp_introduction.tex
Rearrange content

Tropical cyclones, including hurricanes, can have disastrous impacts in the
\ac{US}. A tropical cyclone's high winds can bring health risks
and property damage through structural damage of houses and other buildings,
falling trees, and wind-borne debris~\citep{rappaport2000} and cause power
outages~\citep{liu2005, han2009}, which introduce a number of threats to human
and ecological health, including water quality risks if the outage affects
wastewater treatment plants~\citep{mallin2006}.  Other risks can exist without
severe wind; for example, one study found that most of the direct
hurricane-related deaths in the \ac{US} between 1970 and 1999 occurred in cases
when wind was below hurricane strength, including for Tropical Storms Charley
in 1998 and Alberto in 1994~\citep{rappaport2000}.  Tropical cyclones can
produce excessive rain, especially in certain topographies (e.g., near
mountains), so counties well inland sometimes experience more extreme rain than
coastal counties. Flood risks from tropical cyclones can result from this rain,
although the two risks are not perfectly correlated~\citep{chen2015}. In the
\ac{US}, over half of hurricane-related direct deaths from 1970 to 1999 from
Atlantic basin storms were a result of freshwater flooding~\citep{rappaport2000}. 
Flooding can also degrade water quality~\citep{mallin2006}, which can threaten both 
human and ecological health.

@@

Distance from the tropical cyclone's central track can be easily measured using
widely-available hurricane tracking data. There are, however, a number of
limitations to using distance to assess exposure to tropical cyclones, and
there are reasons to suspect that exposure classifications based on other
tropical cyclone hazards may disagree with distance-based classifications.
Tropical cyclones vary dramatically in size: \ac{US} tropical cyclones have been
observed with radii to maximum winds as small as 20 kilometers and as large as
200 kilometers~\citep{mallin2006, quiring2011variations}. While a number of
tropical cyclone hazards are strongly associated with distance from the
tropical cyclone's center (e.g., wind and, at the coast, storm surge and 
waves~\citep{rappaport2000, kruk2010}), other hazards like dangerous rain, 
floods, and tornadoes can occur well away from the tropical cyclone's central 
track~\citep{rappaport2000, atallah2007, moore2012}.  For example, fatal tropical
cyclone tornadoes, which were linked to over 300 deaths in the \ac{US}  between
1995 and 2009, most often occur 200\,--\,500 kilometers from the tropical cyclone's
center~\citep{moore2012}.

Further, distance-based exposure metrics that use
buffers tend to use an equal buffer distance on each side of the tropical
cyclone track (e.g.,~\citep{czajkowski2011, grabich2015, grabich2016,
zandbergen2009, tansel2010}), but the forces of a tropical cyclone tend to be
distributed around the center in a non-symmetrical way. For example, extreme
winds are more common to the right of the track, where counter-clockwise
cyclonic winds move in concert with the tropical cyclone's forward 
motion~\citep{halverson2015}, and the fatal tornadoes associated with \ac{US} tropical
cyclones between 1995 and 2009 occurred almost exclusively to the right of the
tropical cyclone's track, mostly in the right front quadrant of the tropical
cyclone~\citep{moore2012}. Rain, conversely, is often heaviest to the left of
the tropical cyclone's track, especially when the tropical cyclone interacts
with other weather systems~\citep{atallah2003, atallah2007, zhu2013variations}
or undergoes an extratropical transition~\citep{elsberry2002}.

@@

To investigate this, we measured county-level exposure to tropical cyclones in
all eastern \ac{US} counties using five metrics (
Table~\ref{tab:exposuremetrics}): (1) distance to tropical cyclone track; (2) maximum
sustained wind speed; (3) cumulative rainfall; (4) flood events; and (5)
tornado events.  We assessed exposure at the county level since data on many
potential impacts are available at county-level aggregations (e.g., direct
hurricane-related deaths~\citep{czajkowski2011}; birth outcomes~\citep{grabich2015,
grabich2016}; autism prevalence~\citep{kinney2008}) and
since decisions and policies to prepare for, and respond to, tropical cyclones
are often undertaken at the county level~\citep{zandbergen2009, rappaport2000}.
We explored patterns in these exposure assessments and measured how well
exposure classification agreed across these five metrics in terms of
classifying specific counties as exposed to a tropical cyclone.  Finally, to
make this hazard-specific tropical cyclone exposure data available to other
researchers, we published open source software for county-based hurricane
exposure assessment in \ac{US} counties~\citep{hurricaneexposure}.

>>>>

Tropical cyclones, including hurricanes, can have disastrous impacts in the
\ac{US}. A tropical cyclone's high winds can bring health risks
and property damage through structural damage of houses and other buildings,
falling trees, and wind-borne debris~\citep{rappaport2000} and cause power
outages~\citep{liu2005, han2009}, which introduce a number of threats to human
and ecological health, including water quality risks if the outage affects
wastewater treatment plants~\citep{mallin2006}.  Other risks can exist without
severe wind; for example, one study found that most of the direct
hurricane-related deaths in the \ac{US} between~1970 and~1999 occurred in cases
when wind was below hurricane strength, including for Tropical Storms Charley
in~1998 and Alberto in~1994~\citep{rappaport2000}.  Tropical cyclones can
produce excessive rain, especially in certain topographies (e.g., near
mountains), so counties well inland sometimes experience more extreme rain than
coastal counties. Flood risks from tropical cyclones can result from this rain,
although the two risks are not perfectly correlated~\citep{chen2015}. In the
\ac{US}, over half of hurricane-related direct deaths from~1970 to~1999 from
Atlantic basin storms were a result of freshwater flooding~\citep{rappaport2000}. 
Flooding can also degrade water quality~\citep{mallin2006}, which can threaten both 
human and ecological health.

@@

Distance from the tropical cyclone's central track can be easily measured using
widely-available hurricane tracking data. There are, however, a number of
limitations to using distance to assess exposure to tropical cyclones, and
there are reasons to suspect that exposure classifications based on other
tropical cyclone hazards may disagree with distance-based classifications.
Tropical cyclones vary dramatically in size: \ac{US} tropical cyclones have
been observed with radii to maximum winds as small as~20~\si{\kilo\metre} and as
large as~200~\si{\kilo\metre}~\citep{mallin2006, quiring2011variations}. While a
number of tropical cyclone hazards are strongly associated with distance from
the tropical cyclone's center (e.g., wind and, at the coast, storm surge and
waves~\citep{rappaport2000, kruk2010}), other hazards like dangerous rain,
floods, and tornadoes can occur well away from the tropical cyclone's central
track~\citep{rappaport2000, atallah2007, moore2012}.  For example, fatal
tropical cyclone tornadoes, which were linked to over~300 deaths in the \ac{US}
between~1995 and~2009, most often occur~200\,--\,500~\si{\kilo\metre} from the
tropical cyclone's center~\citep{moore2012}.

Further, distance-based exposure metrics that use
buffers tend to use an equal buffer distance on each side of the tropical
cyclone track (e.g.,~\cite{czajkowski2011, grabich2015, grabich2016,
zandbergen2009, tansel2010}), but the forces of a tropical cyclone tend to be
distributed around the center in a non-symmetrical way. For example, extreme
winds are more common to the right of the track, where counter-clockwise
cyclonic winds move in concert with the tropical cyclone's forward 
motion~\citep{halverson2015}, and the fatal tornadoes associated with \ac{US} tropical
cyclones between~1995 and~2009 occurred almost exclusively to the right of the
tropical cyclone's track, mostly in the right front quadrant of the tropical
cyclone~\citep{moore2012}. Rain, conversely, is often heaviest to the left of
the tropical cyclone's track, especially when the tropical cyclone interacts
with other weather systems~\citep{atallah2003, atallah2007, zhu2013variations}
or undergoes an extratropical transition~\citep{elsberry2002}.

@@

To investigate this, we measured county-level exposure to tropical cyclones in
all eastern \ac{US} counties using five metrics
(Table~\ref{tab:exposuremetrics}): (1)~distance to tropical cyclone track;
(2)~maximum sustained wind speed; (3)~cumulative rainfall; (4)~flood events;
and (5)~tornado events.  We assessed exposure at the county level since data on
many potential impacts are available at county-level aggregations (e.g., direct
hurricane-related deaths~\citep{czajkowski2011}; birth
outcomes~\citep{grabich2015, grabich2016}; autism
prevalence~\citep{kinney2008}) and since decisions and policies to prepare for,
and respond to, tropical cyclones are often undertaken at the county
level~\citep{zandbergen2009, rappaport2000}.  We explored patterns in these
exposure assessments and measured how well exposure classification agreed
across these five metrics in terms of classifying specific counties as exposed
to a tropical cyclone.  Finally, to make this hazard-specific tropical cyclone
exposure data available to other researchers, we published open source software
for county-based hurricane exposure assessment in \ac{US}
counties~\citep{hurricaneexposure}.

### 2019-01-27 writing/ehp_methods.tex
Rearrange content

All counties in the eastern half of the \ac{US} (e.g., Figure~\ref{fig:ivanexposure}), 
as of the 2010 \ac{US} Decennial Census, were included in
the study. The study covered all tracked storms in the \ac{HURDAT2} \citep{landsea2013} 
that came within 250
kilometers of at least one study county between 1988 and 2015 (Figure~S2).
HURDAT2 is a post-storm assessment conducted by the \ac{US} National Hurricane
Center (NHC) and incorporates data from a variety of sources, including
satellite data and, when available, aircraft reconnaissance 
data~\citep{landsea2013, jarvinen1988}. These data typically give measurements of
the tropical cyclone center's location at 6-hour intervals at synoptic times
(i.e., 6:00 am, 12:00 pm, 6:00 pm, and 12:00 am UTC); some landfalling tropical
cyclones have an additional observation at the time of landfall~\citep{landsea2013}.

@@

For each storm, the distance of closest approach was measured for every study county. 
Storm center track location data from \ac{HURDAT2} was 
interpolated using natural cubic splines to 15-minute intervals~\cite{hurricaneexposure}. 
The distance between each county's population mean center, as assessed by the 2010 Decennial
Census~\cite{countycenters}, and each 15-minute interpolated storm center location was
measured using Great Circle (WGS84 ellipsoid) distance~\cite{bivand2013applied}. The 
distance-based exposure metric was based on the minimum value of this storm 
center-to-county distance throughout the period the storm was tracked. The time of 
closest approach for each county-storm pairing was also recorded for use assessing 
rain-, flood-, and tornado-based metrics. To allow matching with data based on local 
time, times were converted from Coordinated Universal Time (UTC) to local 
time~\cite{countytimezones}.

@@

For the rain-based exposure metric, cumulative rainfall was estimated for the
period from two days before to one day after the date of a tropical cyclone's
closest approach to a county. Daily county-level rainfall was determined by
aggregating hourly, 1/8 degree gridded reanalysis data from the North American
Land Data Assimilation System Phase 2 (NLDAS-2) precipitation data 
files~\citep{rui2013nldas}. The NLDAS-2 data integrate satellite-based and land-based
monitoring, applying a land-surface model to create a reanalysis dataset that
is spatially and temporally complete across the continental 
\ac{US}~\citep{rui2013nldas, alhamdan2014environmental}. To aggregate to county-level,
hourly data at each grid point were summed to create a daily rainfall total,
and these grid point rainfall totals were then averaged across all grid points
within a county's 1990 \ac{US} Census boundaries to create a county-level daily
total~\citep{alhamdan2014environmental, cdcwonder}. This county-level
precipitation data are publicly available through the \ac{US} Centers for Disease
Control's Wide-ranging Online Data for Epidemiological Research (WONDER)
database~\citep{cdcwonder, alhamdan2014environmental}. The rainfall-based
exposure metric was only available for tropical cyclones through 2011, the
period for which the county-aggregated reanalysis rainfall data were 
available~\citep{cdcwonder, alhamdan2014environmental}. Validation analysis of this and
other hazard-based exposure data is given in the Supplemental Material.

@@

Ground-based observations of wind speed are problematic during tropical
cyclones, as instruments often fail at high wind speed, while reanalysis data,
often available at hourly or higher resolution, can be too smooth to capture
wind extremes associated with a tropical cyclone. Therefore, to create a
dataset of county-level sustained winds during historical tropical cyclones, we
modeled maximum sustained wind speeds at each county's population mean 
center~\citep{countycenters}. HURDAT2 Best Track data were interpolated from 6-hourly
reported values to 15-minute increments using natural cubic 
splines~\citep{stormwindmodel}, and then sustained wind speed was modeled for each
county center at each 15-minute increment using a double exponential wind speed
model~\citep{willoughby2006parametric} to estimate maximum ground-level
sustained wind speed at each county center~\citep{stormwindmodel}. Asymmetry in
wind speeds around the tropical cyclone center was incorporated into the wind
speed model~\citep{phadke2003modeling, stormwindmodel}. The maximum value of
this modeled wind speed was determined for each county as the maximum windspeed
across the 15-minute incremented modeled values throughout the tropical
cyclone.

@@

To identify flood- and tornado-based exposures to tropical cyclones in \ac{US}
counties, we used event listings from the National Oceanic and Atmospheric
Administration (NOAA)'s Storm Event Database~\citep{stormevents}. For each
tropical cyclone, we identified all events with event types related to flooding
(``Flood", ``Flash Flood", ``Coastal Flood") and tornadoes (``Tornado") and
that occurred in a county within 500 kilometers of the tropical cyclone's track
and within a five-day window centered on the date of the tropical cyclone's
closest approach to the county~\citep{hurricaneexposuredata}. ``Flood", ``Flash
Flood" and ``Tornado" events in this database were reported by county Federal
Information Processing Standard (FIPS) code. ``Coastal Flood" events were
reported by forecast zone; for these, the event was matched to the appropriate
county if possible~\citep{noaastormevents}. While this database has recorded
storm data since 1950, its coverage changed substantially in 1996 to cover a
wider variety of storm events~\citep{stormevents}. We therefore only considered
these metrics of hurricane exposure for tropical cyclones in 1996 and later.

\subsection*{Assessment of tropical cyclone exposure data}

To assess the rainfall estimates from the reanalysis data used in analysis in the the 
main text, we compared cumulative rainfall estimates based on this reanalysis rainfall 
data to rainfall observations from ground-based weather stations in nine sample study 
counties, selected as counties with data available from multiple stations. In these nine
counties, observed rainfall was collected for all storms, 1988\,--\,2011, for the same period 
of two days before to one day after each storm's closest approach, using all stations with
available daily data in the Global Historical Climatology Network throughout 
1988\,--\,2011~\citep{menne2012overview, rnoaa, countyweather}. Agreement between 
measured storm-related rainfall between these two data sources was assessed by 
Spearman's rank correlation.

To validate the metric of county-level wind speed used in the main text, we compared this 
wind metric to estimated wind radii from the revised Atlantic hurricane database (HURDAT2),
available for storms in our study from 2004~\citep{landsea2013}. HURDAT2 gives estimates of
the maximum radii to winds of 64, 50, and 34 knots in each four quadrants of a storm (i.e.,
distance from the storm's center to the furthest point in a quadrant with winds at or above
that speed) at each 6-hour storm observation.

As validation for the flood data, we compared streamflow data from United States (\ac{US})
Geological Survey gages~\citep{usgsgages, countyfloods, dataRetrieval} in nine counties with
tropical cyclone flood classifications based on the NOAA Storm Events Database 
(Figure~\ref{fig:floodcomparison}).

@@

Two of the exposure metrics (flood- and tornado-based) were inherently binary,
since these metrics were based on whether an event was listed in the NOAA Storm
Events database or not.  For the other exposure metrics, each county was
classified as exposed to a tropical cyclone based on whether the exposure
metric exceeded a certain threshold (Table~\ref{tab:exposuremetrics}). We
assessed county-level tropical cyclone exposure in the eastern \ac{US} based on
each exposure metric for all land-falling or near-land Atlantic basin tropical
cyclones. Depending on available exposure data, this assessment included some
or all of the period from 1988 to 2015, a period with 136 tropical cyclones
that made \ac{US} landfall or passed within 250 kilometers (155 miles) of at least
one \ac{US} county (Figure~S2).

We measured agreement between exposure metrics in the classification of a
county as exposed or unexposed to a specific tropical cyclone. For this
measurement, we calculated the within-storm Jaccard 
index~\citep{jaccard1901distribution, jaccard1908nouvelles} between every pair-wise
combination of hazard metrics.  The Jaccard index ($J_s$) measures similarity
between two metrics ($X_{1,s}$ and $X_{2,s}$) for tropical cyclone $s$ as the
proportion of counties in which both of the metrics classify the county as
exposed out of all counties classified as exposed by at least one of the
metrics:

@@

\noindent This metric can range from 0, in the case of no overlap between the counties
classified as exposed based on the two metrics, to 1, in the case that the
two metrics classify exactly the same counties as exposed to the tropical cyclone.

>>>>

All counties in the eastern half of the \ac{US}
(Figure~\ref{fig:ivanexposure}), as of the~2010 \ac{US} Decennial Census, were
included in the study. The study covered all tracked storms in the \ac{HURDAT2}
\citep{landsea2013} that came within~250 \si{\kilo\metre} of at least one study
county between~1988 and~2015 (Figure~S2).  \ac{HURDAT2} is a post-storm
assessment conducted by the \ac{US} \ac{NHC} and incorporates data from a
variety of sources, including satellite data and, when available, aircraft
reconnaissance data~\citep{landsea2013, jarvinen1988}. These data typically
give measurements of the tropical cyclone center's location at~6-\si{\hour} intervals
at synoptic times (i.e., 6:00~am, 12:00~pm, 6:00~pm, and 12:00~am \ac{UTC});
some landfalling tropical cyclones have an additional observation at the time
of landfall~\citep{landsea2013}.

@@

For each storm, the distance of closest approach was measured for every study
county.  Storm center track location data from \ac{HURDAT2} were interpolated
using natural cubic splines to~15-\si{\minute} intervals~\citep{hurricaneexposure}.
The distance between each county's population mean center, as assessed by the
2010 Decennial Census~\citep{countycenters}, and each~15-\si{\minute} interpolated
storm center location was measured using Great Circle (WGS84 ellipsoid)
distance~\citep{bivand2013applied}. The distance-based exposure metric was
based on the minimum value of this storm center-to-county distance throughout
the period the storm was tracked. The time of closest approach for each
county-storm pairing was also recorded for use assessing rain-, flood-, and
tornado-based metrics. To allow matching with data based on local time, times
were converted from \ac{UTC} to local time~\citep{countytimezones}.

@@

For the rain-based exposure metric, cumulative rainfall was estimated for the
period from two days before to one day after the date of a tropical cyclone's
closest approach to a county. Daily county-level rainfall was determined by
aggregating hourly~1/8\si{\degree} gridded reanalysis data from the \ac{NLDAS-2}
precipitation data files~\citep{rui2013nldas}. The \ac{NLDAS-2} data integrate
satellite-based and land-based monitoring, applying a land-surface model to
create a reanalysis dataset that is spatially and temporally complete across
the continental \ac{US}~\citep{rui2013nldas, alhamdan2014environmental}. To
aggregate to county-level, hourly data at each grid point were summed to create
a daily rainfall total, and these grid point rainfall totals were then averaged
across all grid points within a county's~1990 \ac{US} Census boundaries to
create a county-level daily total~\citep{alhamdan2014environmental, cdcwonder}.
This county-level precipitation data are publicly available through the \ac{US}
\ac{CDC}'s \ac{WONDER} database~\citep{cdcwonder, alhamdan2014environmental}.
The rainfall-based exposure metric was only available for tropical cyclones
through~2011, the period for which the county-aggregated reanalysis rainfall
data were available~\citep{cdcwonder, alhamdan2014environmental}.

To assess the rainfall estimates from the reanalysis data used in analysis in
the the main text, we compared cumulative rainfall estimates based on this
reanalysis rainfall data to rainfall observations from ground-based weather
stations in nine sample study counties, selected as counties with data
available from multiple stations. In these nine counties, observed rainfall was
collected for all storms,~1988\,--\,2011, for the same period of two days
before to one day after each storm's closest approach, using all stations with
available daily data in the Global Historical Climatology Network throughout
1988\,--\,2011~\citep{menne2012overview, rnoaa, countyweather}. Agreement
between measured storm-related rainfall between these two data sources was
assessed by Spearman's rank correlation.

@@

Ground-based observations of wind speed are problematic during tropical
cyclones, as instruments often fail at high wind speed, while reanalysis data,
often available at hourly or higher resolution, can be too smooth to capture
wind extremes associated with a tropical cyclone. Therefore, to create a
dataset of county-level sustained winds during historical tropical cyclones, we
modeled maximum sustained wind speeds at each county's population mean
center~\citep{countycenters}. \ac{HURDAT2} Best Track data were interpolated
from~6-\si{\hour} reported values to~15-\si{\minute} increments using natural cubic
splines~\citep{stormwindmodel}, and then sustained wind speed was modeled for
each county center at each~15-\si{\minute} increment using a double exponential wind
speed model~\citep{willoughby2006parametric} to estimate maximum ground-level
sustained wind speed at each county center~\citep{stormwindmodel}. Asymmetry in
wind speeds around the tropical cyclone center was incorporated into the wind
speed model~\citep{phadke2003modeling, stormwindmodel}. The maximum value of
this modeled wind speed was determined for each county as the maximum windspeed
across the~15-\si{\minute} incremented modeled values throughout the tropical
cyclone.

To validate the metric of county-level wind speed used in the main text, we
compared this wind metric to estimated wind radii from \ac{HURDAT2}, available
for storms in our study from~2004~\citep{landsea2013}. \ac{HURDAT2} gives
estimates of the maximum radii to winds of~64,~50, and~34 \si{\knot} in each four
quadrants of a storm (i.e., distance from the storm's center to the furthest
point in a quadrant with winds at or above that speed) at each~6-\si{\hour} storm
observation.

@@

To identify flood- and tornado-based exposures to tropical cyclones in \ac{US}
counties, we used event listings from the National Oceanic and Atmospheric
Administration (NOAA)'s Storm Event Database~\citep{stormevents}. For each
tropical cyclone, we identified all events with event types related to flooding
(``Flood", ``Flash Flood", ``Coastal Flood") and tornadoes (``Tornado") and
that occurred in a county within~500 \si{\kilo\metre} of the tropical cyclone's track
and with a start date within a five-day window centered on the date of the
tropical cyclone's closest approach to the
county~\citep{hurricaneexposuredata}. ``Flood", ``Flash Flood" and ``Tornado"
events in this database were reported by county \ac{FIPS} code. ``Coastal
Flood" events were reported by forecast zone; for these, the event was matched
to the appropriate county if possible~\citep{noaastormevents}. While this
database has recorded storm data since~1950, its coverage changed substantially
in~1996 to cover a wider variety of storm events~\citep{stormevents}. We
therefore only considered these metrics of hurricane exposure for tropical
cyclones in~1996 and later.

As validation for the flood data, we compared streamflow data from \ac{US}
Geological Survey gages~\citep{usgsgages, countyfloods, dataRetrieval} in nine
counties with tropical cyclone flood classifications based on the NOAA Storm
Events Database (Figure~\ref{fig:floodcomparison}).

@@

Two of the exposure metrics (flood- and tornado-based) were inherently binary,
since these metrics were based on whether an event was listed in the NOAA Storm
Events database or not.  For the other exposure metrics, each county was
classified as exposed to a tropical cyclone based on whether the exposure
metric exceeded a certain threshold (Table~\ref{tab:exposuremetrics}). We
assessed county-level tropical cyclone exposure in the eastern \ac{US} based on
each exposure metric for all land-falling or near-land Atlantic basin tropical
cyclones. Depending on available exposure data, this assessment included some
or all of the period from~1988 to~2015, a period with~136 tropical cyclones
that made \ac{US} landfall or passed within~250 \si{\kilo\metre} (155 mi) of at
least one \ac{US} county (Figure~S2).

We measured agreement between exposure metrics in the classification of a
county as exposed or unexposed to a specific tropical cyclone. For this
measurement, we calculated the within-storm Jaccard
index~\citep{jaccard1901distribution, jaccard1908nouvelles} between every
pair-wise combination of hazard metrics.  The Jaccard index~($J_s$) measures
similarity between two metrics ($X_{1,s}$ and~$X_{2,s}$) for tropical
cyclone~$s$ as the proportion of counties in which both of the metrics classify
the county as exposed out of all counties classified as exposed by at least one
of the metrics:

@@

\noindent This metric can range from~0, in the case of no overlap between the
counties classified as exposed based on the two metrics, to~1, in the case that
the two metrics classify exactly the same counties as exposed to the tropical
cyclone.

\subsection*{Case study: Physical exposure of electricity-dependent Medicare
beneficiaries to tropical cyclones}

The outcomes of disasters depend both on the geophysical forces of the disaster
as well as on the vulnerability of the society living in the geographical areas
affected by those forces.~\citep{chakraborty2005population,
anderson2003community, cutter1996vulnerability} As a case study of how
differences in tropical cyclone exposure assessments across different hazard
metrics influence estimates of physical exposures of susceptible populations to
tropical cyclones, we investigated how the use of different metrics influenced
estimates of which eastern \ac{US} counties have the highest expected average
exposures of electricity-dependent Medicare beneficiaries to tropical cyclones.
This subpopulation was selected for this analysis since it may be particularly
susceptible to health impacts from tropical cyclone exposure, especially
through the pathway of storm-associated power outages and evacuations. We
collected data on the number of electricity-dependent Medicare beneficiaries in
each study county from the U.S. Department of Health \& Human Service's emPower
Map~2.0~\citep{empower}. We then calculated the physical exposure of the
electricity-dependent Medicare population in each county, based on tropical
cyclone assessments using each hazard metric,
following~\citep{peduzzi2009assessing}:

\begin{equation}
E_c = F_c * P_c
\end{equation}

\noindent where~$E_c$ is the average yearly physical exposure among
electricity-dependent Medicare beneficiaries in county~$c$ to tropical cyclone
exposures based on a given metric,~$F_c$ is the estimated yearly expected
frequency of tropical cyclone exposures in county~$c$ based on that metric,
and~$P_c$ is the size of the electricity-dependent Medicare population in
county~$c$, as of July~2017. When combined with estimates of vulnerability of a
population to a natural hazard, such measurements of physical exposure can be
used to calculate risk of human losses from the
hazard~\citep{peduzzi2009assessing}.
